\vspace{\baselineskip} The population of long-period transiting exoplanets \vspace{-2\baselineskip}

### 2016-09-19 document/ms.tex
addressed referee point (2)

>>>>

We note that in the above procedure we have not corrected our predictions
for the fact that our search has explicitly excluded KOIs
that host known \kepler\ EBs---if any of these excluded systems show fewer than 
three eclipses and do not present both primary and secondary eclipses, then they 
should also should perhaps count towards the number of EBs we should have 
expected to find in this survey.  However, as the \kepler\ EB catalog does not provide information
on whether both primary and secondary eclipses are detected, we neglect this correction.
We note that this is a conservative decision, in the sense that accounting for the
effect of excluded EBs on our predictions would only further decrease the FPP of 
the planetary signals, as they would be even less likely to be caused by EBs.
